\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2022-02-02 slides/IASD/pres.tex
Update the figures of estimated params

\begin{frame}{Experiments}
  \centering
  \includegraphics[height= 3cm, width=5cm]{figures/likelihood.png} \hspace{1cm} \\
  \vspace{0.5cm}
  \includegraphics[height= 2cm, width=4cm]{figures/beta_learning.png} \hspace{0.7cm}
  \includegraphics[height= 2cm, width=4cm]{figures/beta_estimation.png} \\
  \vspace{0.5cm}
  \includegraphics[height= 2cm, width=4cm]{figures/xi_learning.png} \hspace{0.7cm}
  \includegraphics[height= 2cm, width=4cm]{figures/xi_estimation.png} \\
\end{frame}

>>>>

\begin{frame}{Experiments}
  \includegraphics[height= 1.5cm, width=4cm]{figures/beta_estimation.png} \hspace{0.1cm}
  \includegraphics[height= 1.5cm, width=2.2cm]{figures/xi_estimation.png} \hspace{0.1cm}
  \includegraphics[height= 1.4cm, width=2.2cm]{figures/baseline_estimation.png} \hspace{0.1cm} \\
  \vspace{0.5cm}
  \includegraphics[height= 2cm, width=4cm]{figures/beta_mlmm_learning.png} \hspace{0.7cm}
  \includegraphics[height= 1.5cm, width=4cm]{figures/gamma_estimation.png} \\
  \vspace{0.5cm}
  \hspace{0.2cm}
  \includegraphics[height= 2cm, width=3cm]{figures/beta_learning.png}
  \\
\end{frame}
